Capstone Movielens Report

### 2025-11-13 reports/capstone-movielens.site/05.appendix.Rmd
Functions described: calc_user_movie_effect_MSE.cv, calc_user_movie_effect_RMSE.cv.
Fix for functions' description.

Under the hood, this function internally calls the [train_user_movie_effect](#func.train_user_movie_effect) function described above for every iteration of the _N-Fold Cross-Validation_ applied to the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets]. It also calls internally the [union_cv_results](#func.union_cv_results) function described above in the *Data Helper Functions / [Models Training Functions]* section of this *Appendix* to aggregate the cross-validation results.

@@

Calculates *Mean Squared Error (MSE)* for the *UM Effect (UME) Model* produced by the [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) function call.

@@

Calculates *Mean Squared Error (MSE)* for the *UM Effect (UME) Model* (produced by the [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) function call) using *N-Fold Cross-Validation*.

@@

Calculates *Root Mean Squared Error (RMSE)* for the *UM Effect (UME) Model* (produced by the [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) function call) using *N-Fold Cross-Validation*.

@@

>>>>

Under the hood, this function internally calls the [train_user_movie_effect](#func.train_user_movie_effect) function described above for each iteration of the _N-Fold Cross-Validation_ applied to the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets]. It also calls internally the [union_cv_results](#func.union_cv_results) function described above in the *Data Helper Functions / [Models Training Functions]* section of this *Appendix* to aggregate the cross-validation results.

@@

Calculates *Mean Squared Error (MSE)* for the *UM Effect (UME) Model* produced by the  [train_user_movie_effect](#func.train_user_movie_effect) or [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) function call.

@@

Calculates *Mean Squared Error (MSE)* for the *UM Effect (UME) Model* (produced by the [train_user_movie_effect](#func.train_user_movie_effect) or [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) function call) using *N-Fold Cross-Validation*.

@@

Calculates *Root Mean Squared Error (RMSE)* for the *UM Effect (UME) Model* (produced by the [train_user_movie_effect](#func.train_user_movie_effect) or [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) function call) using *N-Fold Cross-Validation*.

@@

The *RMSE* value calculated for the *UM Effect Model* using the *N-Fold Cross-Validation*, where the `N` is the length of the [`edx_CV` Object].
:::
